An Airdrop That Preserves Recipient Privacy

### 2019-01-10 paper/paper.tex
add 'peanut gallery' package
question about delivering Enc(s) to signer in \S2
question about 'secure' vs 'private' in \S3.1

\documentclass[11pt]{article}
\usepackage[hidelinks]{hyperref}
\usepackage{amsthm,amsmath,amsfonts,amssymb,amstext,mathtools}
\usepackage{fullpage}
\usepackage{macros}

@@

A private airdrop (PAD) system is a triple of efficient algorithms:
\begin{itemize}
\item $\text{sendTokens}(\PK) \to (c, s)$:
Generates a token $c$ to be posted on the blockchain,
and a secret~$s$ given to the recipient via a private channel.
For example, an encryption of $s$ under $\PK$ can be posted
to the blockchain.   The posted encrypted $s$ is not associated with 
the token $c$.

@@

To prove knowledge of the factorization of $n$ the prover
proves knowledge of a $w \in \range{N}$ such that $w^2 \equiv t \pmod{n}$
for some small public prime $t \in \ZZ$, namely $2 \leq t \leq \lambda$.
That is, we provide a ZKPK for the relation
\begin{equation} \label{eq:lang}
  {\cal R}_{g,h} \deq \left\{ \Bigl( (c, t) \in \GG \times \range{\lambda},\ \ 
                              (n, s, w, a) \in \range{N}^4 \Bigr)  \ \ 
        \text{s.t.}\ \ 
                \begin{split}
                        c   & = g^n \cdot h^s \ \ \text{in $\GG$}, \\
                        w^2 & = t + a \cdot n \ \ \text{in $\ZZ$}, \\
                        2 & \leq t \leq \lambda  \ \textrm{a prime}
                \end{split}  \right\}.
\end{equation}
Here $(c, t)$ is a statement and $(n, s, w, a)$ is a witness.
The integer relation $w^2 = t + a\cdot n$ proves that 
$w^2 \equiv t \pmod{n}$, as required.
We note that a ZKPK for~\eqref{eq:lang} proves that $t \in \ZZ$ is a quadratic
residue modulo the committed $n$.  Leaking this bit of information about $n$
does not interfere with the application to a secure airdrop.

>>>>

\documentclass[11pt]{article}
\usepackage[dvipsnames]{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{amsthm,amsmath,amsfonts,amssymb,amstext,mathtools}
\usepackage{fullpage}
\usepackage{macros}
\usepackage[normalem]{ulem}
\usepackage{peanutgallery}

@@

A private airdrop (PAD) system is a triple of efficient algorithms:
\begin{itemize}
\item $\text{sendTokens}(\PK) \to (c, s)$:
Generates a token $c$ to be posted on the blockchain,
and a secret~$s$ given to the recipient via a private channel.
For example, an encryption of $s$ under $\PK$ can be posted
to the blockchain.   The posted encrypted $s$ is not associated with 
the token $c$. 
\RSW{is it necessary to suggest that Enc(s) appear on the blockchain? It could just be posted publicly, since it doesn't need to be remembered for long.}

@@

To prove knowledge of the factorization of $n$ the prover
proves knowledge of a $w \in \range{N}$ such that $w^2 \equiv t \pmod{n}$
for some small public prime $t \in \ZZ$, namely $2 \leq t \leq \lambda$.
That is, we provide a ZKPK for the relation
\begin{equation} \label{eq:lang}
  {\cal R}_{g,h} \deq \left\{ \Bigl( (c, t) \in \GG \times \range{\lambda},\ \ 
                              (n, s, w, a) \in \range{N}^4 \Bigr)  \ \ 
        \text{s.t.}\ \ 
                \begin{split}
                        c   & = g^n \cdot h^s \ \ \text{in $\GG$}, \\
                        w^2 & = t + a \cdot n \ \ \text{in $\ZZ$}, \\
                        2 & \leq t \leq \lambda  \ \textrm{a prime}
                \end{split}  \right\}.
\end{equation}
Here $(c, t)$ is a statement and $(n, s, w, a)$ is a witness.
The integer relation $w^2 = t + a\cdot n$ proves that 
$w^2 \equiv t \pmod{n}$, as required.
We note that a ZKPK for~\eqref{eq:lang} proves that $t \in \ZZ$ is a quadratic
residue modulo the committed $n$.  Leaking this bit of information about $n$
does not interfere with the application to a secure
\RSW{``secure'' $\rightarrow$ ``private''?}
airdrop.
